---
title: "Greenhouse Experiment"
author: "Maryanne Evans"
date: "5/29/2022"
output: pdf_document
---
Library
```{r}
library(ggplot2)
library(readr)
library(tidyverse)
library(dplyr)
library(data.table)
library(tidyr)
library(colorspace)
library(scales)
library(lubridate)
```

Read in data from GitHub, Greenhouse Data
```{r}
GhRD <- read.csv("https://raw.githubusercontent.com/mmevans54/2017-18_Greenhouse_Experiment/master/GH_Dat.csv")
```

```{r}
View(GhRD)
```

Remove Zeros from the analysis
```{r}
#remove zeros from the analysis
#remove zeros from the analysis
nozeroGhRD <- GhRD[ GhRD$Leaf.Number != 0 & 
                      GhRD$Height !=0,]
```

Remove NA values
```{r}
noNAs <- na.omit(nozeroGhRD)
```

#log trans
```{r}
noNAs$logheight=log10(noNAs$Height)
noNAs$logleaf=log10(noNAs$Leaf.Number)
```

View data
```{r}
head(noNAs)
```

```{r}
Rdat <- noNAs %>%
  select (Treatment : logleaf, logheight)%>%
  gather ("Attribute", "Measurement", logleaf : logheight)%>%
  mutate (Attribute = as.factor(Attribute),
          Species = ifelse(Species == "BB", "Blueberry", "Low Bush Cranberry"))
```

```{r}
# Boxplots for Height and Leaf Number, both species
ggplot(data = Rdat, aes(x = Treatment, y = (Measurement)))+
  geom_boxplot(outlier.alpha=0)+
  scale_y_log10() +
  facet_grid(Attribute~Species, scales="free")+
  geom_jitter(height = 0, width = 0.1, alpha =1, aes(col = Treatment))+
  theme(axis.title.y=element_blank())+
  labs(title="Microbial Innoculate Effect on Growth")+
  theme(strip.background = element_blank())+
  scale_x_discrete(limits=c("MD","SD","UD", "Sterile"))+
  theme(legend.position="none")+
  scale_color_manual(values = c("salmon", "violet", "black", "forest green" ))
```

###Statistics###
GhRD2 <- read.csv("GH_RD.csv")
##BB Leaf Number
BlueberryTest=subset(GhRD2,Species=="Blueberry")
BBLNmodel=(aov(Leaf.Number~Treatment, data=GhRD2))
summary(BBLNmodel)
TukeyHSD(BBLNmodel)

##BB Height
BlueberryTest=subset(GhRD2,Species=="Blueberry")
BBHmodel=(aov(Height~Treatment, data=GhRD2))
summary(BBHmodel)
TukeyHSD(BBHmodel)

##LBC Leaf.Number
CranberryTest=subset(GhRD2,Species=="Low Bush Cranberry")
LBLNmodel=(aov(Leaf.Number~Treatment, data=GhRD2))
summary(LBLNmodel)
TukeyHSD(LBLNmodel)

##LBC Height
CranberryTest=subset(GhRD2,Species=="Low Bush Cranberry")
LBHmodel=(aov(Height~Treatment, data=GhRD2))
summary(LBHmodel)
TukeyHSD(LBHmodel)